Periodicity of Geodesic Flows on the Necker Cube Surface

### 2017-10-25 newpaper.tex
102517

\begin{Def}
We call the global affine diffeomorphisms in $\text{Aff}^+(\bM)$ obtained as \textbf{multi-twists of the surface in horizontal and vertical directions} $\mathbf{A}$ and $\mathbf{B}$, respectively.
\\We define the \textbf{derivatives of} $\mathbf{A},\mathbf{B}$ as the matrices 
$D(\mathbf{A})=\mathbf{A}'=\left[ \hspace{1mm} \begin{matrix}
				1 &   2\\
				0 & 1
			\end{matrix}\hspace{1mm}\right] \text{ , and }
			D(\mathbf{B})=\mathbf{B}'=\left[ \hspace{1mm} \begin{matrix}
							1 & 0\\
							 2 & 1
						\end{matrix}\hspace{1mm}\right]$, where $D:\text{Aff}^+(\bM)\rightarrow V(\bM)$.
\end{Def}
These are parabolic elements of $V(\bM)$ that are directly related to the periodic/drift-periodic dichotomy of rational trajectories on the Necker cube surface. To show this directly, we look at how skewing the surface affects our core cylinder curves:

@@

When skewing the surface in the horizontal direction, the horizontal curves are preserved, but the vertical curves obtain two additional positive intersections with adjacent horizontal curves. We work out the $\mathbf{A}, \mathbf{B}$ induced automorphisms of $H_1(\bM,\QQ)$ to be:

@@

\section{Proof of Main Theorem}

>>>>

\begin{Def}
We call the global affine diffeomorphisms in $\text{Aff}^+(\bM)$ obtained as \textbf{multi-twists of the surface in horizontal and vertical directions} $\mathbf{A}$ and $\mathbf{B}$, respectively.
\\We define the \textbf{derivatives of} $\mathbf{A},\mathbf{B}$ as the matrices 
$D(\mathbf{A})=\mathbf{A}'=\left[ \hspace{1mm} \begin{matrix}
				1 &   2\\
				0 & 1
			\end{matrix}\hspace{1mm}\right] \text{ , and }
			D(\mathbf{B})=\mathbf{B}'=\left[ \hspace{1mm} \begin{matrix}
							1 & 0\\
							 2 & 1
						\end{matrix}\hspace{1mm}\right]$, where $D:\text{Aff}^+(\bM)\rightarrow V(\bM)$.
\end{Def}
These are parabolic elements of $V(\bM)$ that are directly related to the dynamical dichotomy of rational trajectories on the Necker cube surface. To show this algebraically, we look at how skewing the surface affects our homology spanning core curves:

@@

When skewing the surface under $\mathbf{A}$ in the horizontal direction, the horizontal curves are preserved, but the vertical curves (odd $\gamma_i$ index) obtain two additional positive intersections with adjacent index (mod 12) horizontal curves. Similarly, the vertical $\mathbf{B}$ skews preserve the vertical curves, but the horizontal curves (even $\gamma_i$ index) obtain two additional \emph{negative} intersections with adjacent index (mod 12) vertical curves. The formulaic expressions of the $\mathbf{A}, \mathbf{B}$ induced automorphisms of $H_1(\bM,\QQ)$ as powers of $k\in\ZZ$ are then:

@@

With all of these in mind we generate the following subgroups:

\begin{Def}
We say $\XX$ is the subgroup of $\text{Aff}^+(\bM)$ generated by $\mathbf{A}$, $\mathbf{B}$.
\end{Def}

\begin{Def}
The images of $\XX$ under their derivative maps to $V(\bM)$ is the subgroup of $V(\bM)$ generated by matrices $\mathbf{A}',$ $\mathbf{B}'$. We denote this group by $\XX'$.
\end{Def}

\begin{Def}
The induced automorphisms of $\XX$ contained in $Aut(H_1(\bM,\QQ))$ is the subgroup generated by $\mathbf{A}_*$, $\mathbf{B}_*$.
\end{Def}
\section{Proof of Main Theorem}
